\begin{thebibliography}{27}
\bibitem{bessa}
Bessa RJ, Miranda V, Botterud A, Wang J, 'Good’ or ’bad’ wind power forecasts: a relative concept, Wind Energy, 14(5), 625–636. doi:10.1002/we.444, 2010.

\bibitem{diebold}
Diebold FX, Mariano RS, Comparing Predictive Accuracy, Journal of Business \& Economic Statistics, 13(3), 253–263. doi:10.1080/07350015.1995.10524599, 1995.

\bibitem{epa}
Environmental Protection Agency (EPA), Office of Air Quality, Planning and Standards, Meteorological Monitoring Guidance for Regulatory modelling Applications, Doc. EPA-454/R-99-005, 2000. 
Online: \url{https://www3.epa.gov/scram001/guidance/met/mmgrma.pdf}

\bibitem{hamill2006}
Hamill, TM and Juras, J, Measuring forecast skill: is it real skill or is it the varying climatology? Q.J.R. Meteorol. Soc., 132: 2905-2923. doi:10.1256/qj.06.25, 2006.

\bibitem{iec}
IEC/ISO 17025:2005(E), General requirements for the competence of testing and calibration laboratories, Version 2, 2005.

\bibitem{jensen}
Jensen 2016: Metrics for evaluation of solar energy forecasts. NCAR Technical Note. NCAR/TN-527+STR doi

\bibitem{jcgm2009}
Joint Committee for Guides in Metrology, Evaluation of measurement data -- An introduction to the "Guide to the expression of uncertainty in measurement" and related documents, JCGM 104:2009, 2009. Online: \url{https://en.wikipedia.org/wiki/Joint_Committee_for_Guides_in_Metrology}

\bibitem{jcgm2008}
Joint Committee for Guides in Metrology, Evaluation of measurement data -- Guide to the expression of uncertainty in measurement. JCGM 100:2008, 2008.

\bibitem{jcgm2008a}
Joint Committee for Guides in Metrology, Evaluation of measurement data -- Supplement 1 to the "Guide to the expression of uncertainty in measurement" -- Propagation of distributions using a Monte Carlo method, JCGM 101:2008, 2008a.

\bibitem{jcgm2011}
Joint Committee for Guides in Metrology, Evaluation of measurement data -- Supplement 2 to the "Guide to the expression of uncertainty in measurement" -- Propagation of distributions using a Monte Carlo method, JCGM 102:2011, 2011.

\bibitem{jcgm2012}
Joint Committee for Guides in Metrology, Evaluation of measurement data -- The role of measurement uncertainty in conformity assessment, JCGM 106:2012, 2012.
\bibitem{lerch2017}
Lerch S, Thorarinsdottir TL, Ravazzolo F and Gneiting T, Forecaster’s Dilemma: Extreme Events and Forecast Evaluation, Statistical Science, 32 $(1)$, pp106-127, 2017.

\bibitem{mahmood2017}
Mahmood, R., Boyles, R., Brinson, K., Fiebrich, C., Foster, S., Hubbard, K., Robinson, D., Andresen, J., & Leathers, D. (2017). Mesonets: Mesoscale Weather and Climate Observations for the United States, Bulletin of the American Meteorological Society, 98(7), 1349-1361. Retrieved Jul 9, 2021, from \url{https://journals.ametsoc.org/view/journals/bams/98/7/bams-d-15-00258.1.xml}

\bibitem{madsen2005}
Madsen H., Pinson P., Kariniotakis G., Nielsen HA, Nielsen TS., Standardizing the Performance Evaluation of Short-Term Wind Power Prediction Models, Wind Engineering, 29(6), 475–489. doi:10.1260/030952405776234599, 2005.

\bibitem{moehrlen2017}
C. M\"ohrlen, C. Collier, J. Zack, J. Lerner, Can Benchmarks and Trials Help Develop new Operational Tools for Balancing Wind Power?, Prog. 16th Workshop on Large-Scale Integration of Wind Power into Power Systems as well as on Transmission Networks for Offshore Wind Power Plant , Berlin (DE), 26-29 June 2017.
Online Access: http://www.ieawindpowerforecasting.dk/publications

\bibitem{moehrlen2018}
M\"ohrlen, C. Zack, J., Lerner, J, Tuohy, A., Browell, J., Messner, J.W., Collier, C.,  Giebel, G., Recommended practices for the implementation of wind power forecasting solutions. Part 2\&3: Designing and executing forecasting benchmarks and trials and evaluation of forecast, Proc. 17th International Workshop on Large-Scale Integration of Wind Power into Power Systems as well as on Transmission Networks for Offshore Wind Power Plant, Stockholm, Sweden, October 2018. Online: \url{http://download.weprog.com/wiw18-160_recommended-practice_benchmark-evaluation.pdf}

\bibitem{murphy}
Murphy 1993: What is a Good Forecast? An Essay on the Nature of Goodness in Weather Forecasting. doi

\bibitem{pinsen}
Pinson P, Girard R, Evaluating the quality of scenarios of short-term wind power generation, Applied Energy, 96, 12–20. doi:10.1016/j.apenergy.2011.11.004. Smart Grids, 2012.

\bibitem{wilks2011}
Wilks 2011: Statistical Methods in the Atmospheric Sciences, Third Edition.

\bibitem{zhang2015}
Zhang 2015: A suite of metrics for assessing the performance of solar power forecasting. Solar Energy 111, 157.

\bibitem{vogt2018}
Vogt, S., Braun, A., Koch, J., Jost, D., Dobschinski, R.J.. Benchmark of Spatio-temporal Shortest-Term Wind Power Forecast Models, Proc. of the 17th International workshop on large scale integration of wind power into power systems as well as on transmission networks for offshore wind power plants, Stockholm, 2018.

\bibitem{anemosplus}
Anemos.Plus Project DELIVERABLE D-1.3, Towards the definition of a standardised evaluation protocol for probabilistic wind power forecasts, 2012. \\
Online available: \url{http://www.anemos-plus.eu/images/pubs/deliverables/aplus.deliverable_d1.3-protocol_v1.5.pdf}

\bibitem{gensler}
Gensler, A., Sick, B., Vogt, S., A Review of Deterministic Error Scores and Normalization Techniques for Power Forecasting Algorithms, 2016 IEEE Symposium Series on Computational Intelligence (SSCI), Athens, 2016, pp. 1-9. DOI: 10.1109/SSCI.2016.7849848, 2016. Online: \url{https://www.sciencedirect.com/science/article/pii/S0169207008001003}

\bibitem{jensen}
Jensen, T., Fowler, T., Brown, B. Lazo, J., Haupt S.E. (2016), Metrics for evaluation of solar energy forecasts, NCAR Technical Note NCAR/TN-527+STR. Online available: \url{http://opensky.ucar.edu/islandora/object/technotes:538}

\bibitem{frias}
Fri\a'as Peredes, L., Stoffels, N., Statistical analysis of wind power and prediction errors for selected test areas, EU 7th Framework project Safewind, Deliverable Dp-7.1. Statistical analysis of wind power and prediction errors for selected test areas. Online available: \url{http://www.safewind.eu/images/Articles/Deliverables/swind.deliverable_dp-7.1_statistical_analysis_v1.6.pdf}

\bibitem{sanchez2008}
Sa\a'nchez, I.: Adaptive combination of forecasts with application to wind energy. International Journal of Forecasting 24(4), pp. 679–693, 2008. Online: \url{https://doi.org/10.1016/j.ijforecast.2008.08.008}

\bibitem{pahlow2008}
Pahlow, M. , M{\"o}hrlen, C., J{\o}rgensen J.U., Application of Cost Functions for Large Scale Integration of Wind Power using a Multi-Scheme Ensemble Prediction Technique, Optimization Advances in Electric Power Systems, Nova Publishers, ISBN: 978-1-60692-613-01, 2008. 

\bibitem{moehrlen2014}
M{\"o}hrlen, C., J{\o}rgensen J.U., Reserve forecasting for enhanced Renewable Energy management, Proc. 12th Int. Workshop on Large-Scale Integration of Wind Power into Power Systems as well as on Transmission Networks for Offshore Wind Farms, Berlin, 2014.

\bibitem{richardson2000}
Richardson, D.S., 2000: Skill and relative economic value of the ECMWF ensemble prediction system. Quart. J. Royal Met. Soc., 126, 649-667.

\bibitem{wilks2001}
Wilks, D.S., 2001: A skill score based on economic value for probability forecasts. Meteorol. Appl., 8, 209-219.

\bibitem{wmoguide1950}
World Meteorological Organization.  (1950).  Guide to meteorological instruments and methods of observation.  \url{http://www.wmo.ch/pages/prog/www/IMOP/publications/WMO-8-Guide-contents.html}

\bibitem{wmoguide1969}
World Meteorological Organization.  (1969).  Guide to meteorological instruments and methods of observation.  \url{http://www.wmo.ch/pages/prog/www/IMOP/publications/WMO-8-Guide-contents.html}

\bibitem{wmoguide1983}
World Meteorological Organization.  (1983).  Guide to meteorological instruments and methods of observation.  \url{http://www.wmo.ch/pages/prog/www/IMOP/publications/WMO-8-Guide-contents.html}

\bibitem{wmoguide2008}
World Meteorological Organization.  (2008).  Guide to meteorological instruments and methods of observation.  \url{http://www.wmo.ch/pages/prog/www/IMOP/publications/WMO-8-Guide-contents.html}

\bibitem{wmoguide2018}
World Meteorological Organization.  (2018).  Guide to meteorological instruments and methods of observation.  \url{http://www.wmo.ch/pages/prog/www/IMOP/publications/WMO-8-Guide-contents.html}

\end{thebibliography}